\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{cases}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{grffile}
\usepackage{setspace}

%\setlength\parindent{0pt}

\author{Xiaohui Chen \\EID: xc2388}
\title{M 362K Reflection Essay}


\begin{document}
\maketitle

I am glad that I registered Professor Maxwell's class. In his class, I not only learned unprecedented knowledge about probability, but also learned how to put probability into real lives.

I do believe that I have a satisfying performance in this class. By doing the pre-class homework and post-class homework, I can fully understand the materials in class. In group problems, I always take the lead by finishing the problem in the shortest time and help my peers. Learning through group cooperation is definitely effective and efficient. When I make mistakes, my peers always point them out and help me improve myself. Undoubtedly, I always do the same thing. Even though we are technically competitors struggling to get higher grades, cooperation is necessary. In fact, group study helps everyone improve themselves.

As I mentioned before, the knowledge I learned is plenty. Also, it is very useful. For example, the Bayes' Theorem is useful for the insurance companies to decide the premium for their customers. In addition, it is used widely in Machine Learning. Through the Bayes' Theorem, a machine can create a Bayes' model such that it can make decisions through observation. As a student majoring in computer science, the knowledge I learned in this class will definitely aid my career in the future.

To be honest, I really like this course. Professor Maxwell demonstrates how indefinite our lives can be. For example, Professor Maxwell sometime uses a dice to decide which homework assignment we ought to turn in. This is very interesting for me because I always finish all my homework on time. Since I always meet Professor Maxwell's requirement, there is nothing I am afraid of and I will never pray for not handing in any assignments. Sincerely, this is one of the favorite courses I ever taken.

As for the midterm, I am sure that I will have a good performance if I review the textbook, homework and class materials. All of the class materials are pretty useful and so I won't miss any of them. Also, I will attend group studies and try to pick up anything I left behind, if any. I am confident that I will get a satisfying result with my eagerness to study and through preparation.

In conclusion, I am really thankful to Professor Maxwell for providing me such a precious opportunity to learn. I am confident that this course will provide me unimaginable positive impacts, both to my study and to my future life.

\end{document}